\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-13 paper/sp.tex
refs

We take the \apogee\ (HOGG CITE) spectral data
from \sdssiv\ (\citealt{sdssiv}) \acronym{DR14} (\citealt{dr14}).
Because we want to make a purely linear model, which has very little capacity,
we restrict our consideration to a small region in stellar parameter space.
We cut the \apogee\ data down to the range $0<\logg<2.2$, which isolates
stars that are more luminous than the red clump.
The \apogee\ pipeline $\logg$ values (which we use) have uncertainties but
this cut leads to a clean sample of luminous red giants, and it is a cut
that is only on spectral properties of the stars (and not photometry nor astrometry).

@@

Although the model, training, and prediction make no use whatsoever about stellar
models, we did use stellar models indirectly to select the Parent Sample of stars:
We used the \apogee\ pipeline surface-gravity $\logg$ measurements.
This tiny use of stellar models could have been obviated by selecting stars not
on the basis of the derived physical parameter, but instead selecting stars to
be similar, observationally, in the spectral space.
That would have lead to a clean sample and made the project independent completely
of stellar models.

@@

\begin{thebibliography}{}
\bibitem[Abolfathi \etal(2018)]{dr14} Abolfathi, B., Aguado, D.~S., Aguilar, G., \etal\ 2018, \apjs, 235, 42 
\bibitem[Astropy Collaboration \etal(2013)]{astropy} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., \etal\ 2013, \aap, 558, A33 
\bibitem[Astropy Collaboration \etal(2018)]{astropy2} The Astropy Collaboration, Price-Whelan, A.~M., Sip{\H o}cz, B.~M., \etal\ 2018, arXiv:1801.02634 
\bibitem[Bailer-Jones \etal(2018)]{calj} Bailer-Jones, C.~A.~L., Rybizki, J., Fouesneau, M., Mantelet, G., \& Andrae, R.\ 2018, \aj, 156, 58 
\bibitem[Blanton \etal(2017)]{sdssiv} Blanton, M.~R., Bershady, M.~A., Abolfathi, B., \etal\ 2017, \aj, 154, 28 
\bibitem[Casey \etal(2016)]{casey} Casey, A.~R., Hogg, D.~W., Ness, M., \etal\ 2016, arXiv:1603.03040 
\bibitem[Ho \etal(2017)]{ho} Ho, A.~Y.~Q., Ness, M.~K., Hogg, D.~W., \etal\ 2017, \apj, 836, 5 
\bibitem[Hogg(2018)]{gaialf} Hogg, D.~W.\ 2018, arXiv:1804.07766
\bibitem[Hunter(2007)]{matplotlib} Hunter, J.~D.\ 2007, CISE, 9(3), 90
\bibitem[Jones \etal(2001)]{scipy} Jones, E., Oliphant, E., Peterson, P. \etal\ 2001, \url{http://www.scipy.org/}
\bibitem[Kollmeier \etal(2017)]{sdssv} Kollmeier, J.~A., Zasowski, G., Rix, H.-W., \etal\ 2017, arXiv:1711.03234 
\bibitem[Lindegren \etal(2018)]{lindegren} Lindegren, L., Hernandez, J., Bombrun, A., \etal\ 2018, arXiv:1804.09366 
\bibitem[Lutz \& Kelker(1973)]{lk} Lutz, T.~E., \& Kelker, D.~H.\ 1973, \pasp, 85, 573 
\bibitem[Martig \etal(2016)]{martig} Martig, M., Fouesneau, M., Rix, H.-W., \etal\ 2016, \mnras, 456, 3655 
\bibitem[Ness \etal(2015)]{cannon} Ness, M., Hogg, D.~W., Rix, H.-W., Ho, A.~Y.~Q., \& Zasowski, G.\ 2015, \apj, 808, 16 
\bibitem[Ness \etal(2016)]{nessage} Ness, M., Hogg, D.~W., Rix, H.-W., \etal\ 2016, \apj, 823, 114 
\bibitem[Ness \etal(2018)]{nessdopp} Ness, M., Rix, H.-W., Hogg, D.~W., \etal\ 2018, \apj, 853, 198 
\bibitem[Oliphant(2006)]{numpy} Oliphant, T.~E.\ 2006, \emph{A guide to NumPy}, Trelgol Publishing
\bibitem[P\'erez \& Granger(2007)]{ipython} P\'erez, F. \& Granger, B.~E.\ 2007, CISE, 9(3), 29
\bibitem[Skrutskie \etal(2006)]{zmass} Skrutskie, M.~F., Cutri, R.~M., Stiening, R., \etal\ 2006, \aj, 131, 1163 
\end{thebibliography}

>>>>

We take the \apogee\ (\citealt{aapogee, wapogee, apogee}) spectral data
from \sdssiv\ (\citealt{sdssiv}) \acronym{DR14} (\citealt{dr14}).
Because we want to make a purely linear model, which has very little capacity,
we restrict our consideration to a small region in stellar parameter space.
We cut the \apogee\ data down to the range $0<\logg<2.2$, which isolates
stars that are more luminous than the red clump.
The \apogee\ pipeline $\logg$ values (which we use) have uncertainties but
this cut leads to a clean sample of luminous red giants, and it is a cut
that is only on spectral properties of the stars (and not photometry nor astrometry).

@@

Although the model, training, and prediction make no use whatsoever about stellar
models, we did use stellar models indirectly to select the Parent Sample of stars:
We used the \apogee\ pipeline (\citealt{aspcap}) surface-gravity $\logg$ measurements.
This tiny use of stellar models could have been obviated by selecting stars not
on the basis of the derived physical parameter, but instead selecting stars to
be similar, observationally, in the spectral space.
That would have lead to a clean sample and made the project independent completely
of stellar models.

@@

\begin{thebibliography}{}
\bibitem[Abolfathi \etal(2018)]{dr14} Abolfathi, B., Aguado, D.~S., Aguilar, G., \etal\ 2018, \apjs, 235, 42 
\bibitem[Allende Prieto \etal(2008)]{aapogee} Allende Prieto, C., Majewski, S.~R., Schiavon, R., \etal\ 2008, Astronomische Nachrichten, 329, 1018 
\bibitem[Astropy Collaboration \etal(2013)]{astropy} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., \etal\ 2013, \aap, 558, A33 
\bibitem[Astropy Collaboration \etal(2018)]{astropy2} The Astropy Collaboration, Price-Whelan, A.~M., Sip{\H o}cz, B.~M., \etal\ 2018, arXiv:1801.02634 
\bibitem[Bailer-Jones \etal(2018)]{calj} Bailer-Jones, C.~A.~L., Rybizki, J., Fouesneau, M., Mantelet, G., \& Andrae, R.\ 2018, \aj, 156, 58 
\bibitem[Blanton \etal(2017)]{sdssiv} Blanton, M.~R., Bershady, M.~A., Abolfathi, B., \etal\ 2017, \aj, 154, 28 
\bibitem[Casey \etal(2016)]{casey} Casey, A.~R., Hogg, D.~W., Ness, M., \etal\ 2016, arXiv:1603.03040 
\bibitem[Garc{\'{\i}}a P{\'e}rez \etal(2016)]{aspcap} Garc{\'{\i}}a P{\'e}rez, A.~E., Allende Prieto, C., Holtzman, J.~A., \etal\ 2016, \aj, 151, 144 
\bibitem[Ho \etal(2017)]{ho} Ho, A.~Y.~Q., Ness, M.~K., Hogg, D.~W., \etal\ 2017, \apj, 836, 5 
\bibitem[Hogg(2018)]{gaialf} Hogg, D.~W.\ 2018, arXiv:1804.07766
\bibitem[Hunter(2007)]{matplotlib} Hunter, J.~D.\ 2007, CISE, 9(3), 90
\bibitem[Jones \etal(2001)]{scipy} Jones, E., Oliphant, E., Peterson, P. \etal\ 2001, \url{http://www.scipy.org/}
\bibitem[Kollmeier \etal(2017)]{sdssv} Kollmeier, J.~A., Zasowski, G., Rix, H.-W., \etal\ 2017, arXiv:1711.03234 
\bibitem[Lindegren \etal(2018)]{lindegren} Lindegren, L., Hernandez, J., Bombrun, A., \etal\ 2018, arXiv:1804.09366 
\bibitem[Lutz \& Kelker(1973)]{lk} Lutz, T.~E., \& Kelker, D.~H.\ 1973, \pasp, 85, 573 
\bibitem[Majewski \etal(2017)]{apogee} Majewski, S.~R., Schiavon, R.~P., Frinchaboy, P.~M., \etal\ 2017, \aj, 154, 94 
\bibitem[Martig \etal(2016)]{martig} Martig, M., Fouesneau, M., Rix, H.-W., \etal\ 2016, \mnras, 456, 3655 
\bibitem[Ness \etal(2015)]{cannon} Ness, M., Hogg, D.~W., Rix, H.-W., Ho, A.~Y.~Q., \& Zasowski, G.\ 2015, \apj, 808, 16 
\bibitem[Ness \etal(2016)]{nessage} Ness, M., Hogg, D.~W., Rix, H.-W., \etal\ 2016, \apj, 823, 114 
\bibitem[Ness \etal(2018)]{nessdopp} Ness, M., Rix, H.-W., Hogg, D.~W., \etal\ 2018, \apj, 853, 198 
\bibitem[Oliphant(2006)]{numpy} Oliphant, T.~E.\ 2006, \emph{A guide to NumPy}, Trelgol Publishing
\bibitem[P\'erez \& Granger(2007)]{ipython} P\'erez, F. \& Granger, B.~E.\ 2007, CISE, 9(3), 29
\bibitem[Skrutskie \etal(2006)]{zmass} Skrutskie, M.~F., Cutri, R.~M., Stiening, R., \etal\ 2006, \aj, 131, 1163 
\bibitem[Wilson \etal(2010)]{wapogee} Wilson, J.~C., Hearty, F., Skrutskie, M.~F., \etal\ 2010, \procspie, 7735, 77351C 
\end{thebibliography}
